PCA on Finnish Municipalities

### 2022-04-09 MSA-Project.Rmd
Added distribution plots

---
title: "PCA on Finnish Municipalities"
author: "Niko Miller"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: 
  pdf_document:
    keep_tex: false
    number_sections: true
    fig_caption: true
    citation_package: natbib
    extra_dependencies: ["float"]
bibliography: references.bib
header-includes:
- \pagenumbering{gobble}
- \usepackage{amsmath}
- \usepackage{amssymb}
- \usepackage{amsfonts}
- \usepackage{mathtools}
- \usepackage{graphicx}
- \usepackage{placeins}
- \usepackage{wrapfig}
- \usepackage{framed}
- \usepackage[font={small,it}]{caption}
- \usepackage[font={small,it}]{subcaption}
- \usepackage{hyperref}
- \usepackage[labelsep=period]{caption}
- \usepackage[labelfont=bf]{caption}
- \captionsetup{justification=raggedright,singlelinecheck=false}

@@

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(summarytools)
library(pxweb)

@@

## Descriptive Statistics

@@

@@

>>>>

---
title: "PCA on Finnish Municipalities"
author: "Niko Miller"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: 
  pdf_document:
    keep_tex: false
    number_sections: true
    fig_caption: true
    citation_package: natbib
    # extra_dependencies: ["float"]
bibliography: references.bib
header-includes:
- \pagenumbering{gobble}
- \usepackage{amsmath}
- \usepackage{amssymb}
- \usepackage{amsfonts}
- \usepackage{mathtools}
- \usepackage{graphicx}
- \usepackage{placeins}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{framed}
- \usepackage[font={small,it}]{caption}
- \usepackage[font={small,it}]{subcaption}
- \usepackage{hyperref}
- \usepackage[labelsep=period]{caption}
- \usepackage[labelfont=bf]{caption}
- \captionsetup{justification=raggedright,singlelinecheck=false}

@@

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(summarytools)
library(pxweb)
library(ggplot2)
library(reshape2)

@@

### Descriptive Statistics

@@

### Distribution Plots

ages <- muni.latest %>% 
  select(Prop.Below15, Prop.15to64, Prop.Over64)
ages <- melt(ages)

living <- muni.latest %>% 
  select(Prop.Households.rowSmall, Prop.Households.Rent)
living <- melt(living)

employment <- muni.latest %>% 
  select(Empl.Rate, Prop.Unempl, Prop.Pension)
employment <- melt(employment)

sectors <- muni.latest %>% 
  select(Prop.Primary.Sector, Prop.Secondary.Sector, Prop.Services.Sector)
sectors <- melt(sectors)

```{r, echo=FALSE, fig.cap='Probability density estimates for age groups', position, out.width='80%'}

ggplot(ages, aes(x=value, fill=variable)) + geom_density(alpha = .25, adjust = .75) + theme_bw() +
  scale_fill_manual( values = c("#dde318","#3dbc74","#440154")) +
  labs(x = "Percentage (%) of Population", y = "Density", fill = "Variable", title = "Age Groups") +
  theme(legend.position = "right", legend.text = element_text(size = 9))

```{r, echo=FALSE, fig.cap='Probability density estimates for living types', out.width='80%'}

ggplot(living, aes(x=value, fill=variable)) + geom_density(alpha = .25, adjust = .75) + theme_bw() +
  scale_fill_manual( values = c("#dde318","#3dbc74","#440154")) +
  labs(x = "Percentage (%) of Population", y = "Density", fill = "Variable", title = "Living Types") +
  theme(legend.position = "right", legend.text = element_text(size = 9))

```{r, echo=FALSE, fig.cap='Probability density estimates for Employment Groups', out.width='80%'}

ggplot(employment, aes(x=value, fill=variable)) + geom_density(alpha = .25, adjust = .75) + theme_bw() +
  scale_fill_manual( values = c("#dde318","#3dbc74","#440154")) +
  labs(x = "Percentage (%) of Population", y = "Density", fill = "Variable", title = "Employment Groups") +
  theme(legend.position = "right", legend.text = element_text(size = 9))

```{r, echo=FALSE, fig.cap='Probability density estimates for Economic Sectors', out.width='80%'}

ggplot(living, aes(x=value, fill=variable)) + geom_density(alpha = .25, adjust = .75) + theme_bw() +
  scale_fill_manual( values = c("#dde318","#3dbc74","#440154")) +
  labs(x = "Percentage (%) of Population", y = "Density", fill = "Variable", title = "Economic Sectors") +
  theme(legend.position = "right", legend.text = element_text(size = 9))

@@

### Pearson's Correlation

- Correlation heatmap here
